Follow-up Samples

### 2017-02-20 submission/manuscript_outline_20161024.tex

\textbf{Figure 1: General Differences between the Adenoma or Carcinoma
Group.} A) A significant difference was found between the adenoma and
carcinoma group for thetayc (P-value = 0.000472). B) A significant
difference was found between the adenoma and carcinoma group for change
in FIT measurement (P-value = 2.15e-05). C) NMDS of the initial and
follow up samples for the Adenoma group. D) NMDS of the initial and
follow up samples for the Carcinoma group. For C) and D) the teal
represents initial samples and the pink represents follow up samples.

\textbf{Figure 2: Previously Associated CRC Bacteria in Initial and
Follow up Samples.} A) Carcinoma initial and follow up samples had an
observed significant difference in initial and follow up sample for the
OTUs classified as \emph{Parvimonas micra} (P-value = 0.0116) and
\emph{Porphyromonas asaccharolytica} (P-value = 0.00842). B) Adenoma
initial and follow up samples. There were no significant differences
between initial and follow up.

\textbf{Figure 3: The Lesion Model.} A) ROC Curve: The shaded areas
represents the range of values of a 100 different 80/20 splits of the
test set data and the blue line represents the model using 100\% of the
data set and what was used for subsequent classification. B) Summary of
Important Variables. MDA of the most important variables in the lesion
model. The black point represents the median and the different colors
are the different runs up to 100. C) Positive probability change from
initial to follow up sample in those with carcinomaA) Lesion model. D)
Positive probability change from initial to follow up sample if those
with adenoma or Screen Relevant Neoplasia (SRN)

\textbf{Figure 4: The Initial Sample Model.} A) ROC Curve: The shaded
areas represents the range of values of a 100 different 80/20 splits of
the test set data and the blue line represents the model using 100\% of
the data set and what was used for subsequent classification. B) Summary
of Important Variables. MDA of the most important variables in the
initial sample model. The black point represents the median and the
different colors are the different runs up to 100. C) Positive
probability change from initial to follow up sample in those with
carcinoma. D) Positive probability change from initial to follow up
sample if those with adenoma or Screen Relevant Neoplasia (SRN).

@@

>>>>

\textbf{Figure 1: General Differences between the Adenoma and Carcinoma
Group.} A) A significant difference was found between the adenoma and
carcinoma group for thetayc (P-value = 0.000472). B) A significant
difference was found between the adenoma and carcinoma group for change
in FIT measurement (P-value = 2.15e-05). C) NMDS of the initial and
follow up samples for the Adenoma group. D) NMDS of the initial and
follow up samples for the Carcinoma group. For C) and D) the teal
represents initial samples and the pink represents follow up samples.

\textbf{Figure 2: Previously Associated CRC Bacteria in Initial and
Follow Up Samples.} A) Carcinoma initial and follow up samples had an
observed significant difference in initial and follow up sample for the
OTUs classified as \emph{Parvimonas micra} (P-value = 0.0116) and
\emph{Porphyromonas asaccharolytica} (P-value = 0.00842). B) Adenoma
initial and follow up samples. There were no significant differences
between initial and follow up (P-value = 0.37.

\textbf{Figure 3: The Lesion Model.} A) ROC curve: The shaded areas
represents the range of values of a 100 different 80/20 splits of the
test set data and the blue line represents the model using 100\% of the
data set and what was used for subsequent classification. B) Summary of
Important Variables. MDA of the most important variables in the lesion
model. The black point represents the mean and the different colors are
the values of each different run up to 100. C) Positive probability
change from initial to follow up sample in those with carcinoma. D)
Positive probability change from initial to follow up sample if those
with adenoma or advanced adenoma (Screen Relevant Neoplasia (SRN)).

\textbf{Figure 4: The Initial Sample Model.} A) ROC curve: The shaded
areas represents the range of values of a 100 different 80/20 splits of
the test set data and the blue line represents the model using 100\% of
the data set and what was used for subsequent classification. B) Summary
of Important Variables. MDA of the most important variables in the
initial sample model. The black point represents the mean and the
different colors are the values of each different run up to 100. C)
Positive probability change from initial to follow up sample in those
with carcinoma. D) Positive probability change from initial to follow up
sample of those with adenoma or advanced adenoma (Screen Relevant
Neoplasia (SRN)).

@@

A detailed and reproducible description of how the data were processed
and analyzed can be found at
\url{https://github.com/SchlossLab/Sze_followUps_2017}. Raw sequences
have been deposited into the NCBI Sequence Read Archive (SRP062005 and
SRP096978) and the necessary metadata can be found at
\url{https://www.ncbi.nlm.nih.gov/Traces/study/} and searching the
respective SRA study accession.
